Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
related work

There is no previous work on types for the R programming language. We take
inspiration in the above mentioned works but focus on adapting them to our
target language.

>>>>

Recent work has gone into adding types to Python, the other eminent data science language.
Typilus is an interesting piece of recent work which explores using neural networks to infer types for Python programs~\cite{allamanis2020typilus}, and Python itself added support for type hints in Python 3.5~\cite{pythonspectypes}.
There is no previous work on types for the R programming language. We take
inspiration in the above mentioned works but focus on adapting them to our
target language.
